---
output: 
  flexdashboard::flex_dashboard:
    navbar:
      - { title: "Main page", href: "file:///O:/Risk/interactive_scorecards_dashboard/title_page.html", align: right }
 
params:
  data: a_nonpayroll_ros_1 
 
title: "`r toupper(params$data)`"
---
 
 
```{r setup, include=FALSE}
 
# libs -----------------
library(flexdashboard)
library(ggplot2)
library(plotly)
library(tidyverse)
library(lubridate)
library(plotROC)
library(dygraphs)
library(highcharter)
library(haven)
library(zoo)
 
 
# paths for tables ------------------------
models_tables_path <- c("")
meta_data_path <- c("")
 
# funtions loading
R.utils::sourceDirectory("")
 
 
# model's table --------------------------
model_table <- read_sas(paste0(models_tables_path, params$data, ".sas7bdat"), NULL)
names(model_table) <- tolower(names(model_table))
 
# meta_data data -------------------------
models <- read_delim(paste0(meta_data_path,"models.csv"), ";", 
                     escape_double = FALSE, trim_ws = TRUE)
 
vars_discr <- read_csv(paste0(meta_data_path,"vars.csv"))
 
 
 
```
 
 
 
Discriminative Power
=====================================  
 
Column {data-width= 50}
-------------------------------------
 
### Discriminative power dynamics
    
```{r out.width = 9, out.height = 5}
# Gini and Auc calculations by year_quarter
gini_dynamics <- model_table %>% 
  mutate(max_dr12 = as.numeric(max_dr12)) %>%
  filter(is.na(max_dr12) == F) %>% 
  select(score, max_dr12, consideration_date) %>% 
  mutate(report_date =  as.Date( as.yearqtr(consideration_date), frac = 1)) %>% 
  group_by(report_date) %>% 
  summarise(gini  = round(fastAUC(score, max_dr12) * 2 - 1, 2)) %>% 
  dplyr::ungroup() %>% 
  as.data.frame() 
 
gini_dynamics_plot <- ggplot(gini_dynamics, aes(x = ymd(report_date), y = gini, group=1, na.rm=T,
                                                text = paste('Gini:', gini ,
                                                            '<br> Reporting date: ', as.Date(report_date)))) + 
                        geom_rect(xmin = as.numeric(min(gini_dynamics$report_date) - 300),
                                  xmax = as.numeric(max(gini_dynamics$report_date)) + 300, 
                                  ymin=.0, 
                                  ymax=.2, 
                                  fill="#C37887", alpha=.2) +
                        geom_rect(xmin = as.numeric(min(gini_dynamics$report_date) - 300),
                                  xmax = as.numeric(max(gini_dynamics$report_date)) + 300, 
                                  ymin=.2, 
                                  ymax=.5, 
                                  fill="#F4EB6E", alpha=.2) +
                        geom_rect(xmin = as.numeric(min(gini_dynamics$report_date)) - 300,
                                  xmax = as.numeric(max(gini_dynamics$report_date)) + 300, 
                                  ymin=.5, 
                                  ymax= 1, 
                                  fill="#7BA363", alpha=.2) +
                        geom_line() + 
                        geom_point() +
                        ylim(min(gini_dynamics$gini) - 0.1, max(gini_dynamics$gini) + 0.1) +
                        xlim(min(gini_dynamics$report_date), max(gini_dynamics$report_date)) + 
                        xlab("Reporting date") + 
                        ylab("Gini coefficient") +  
                        theme_bw()
 
 
 
 
 
 
 
ggplotly(gini_dynamics_plot, tooltip = c("text"))
 
 
 
```
 
 
### Scores distribution for good and bad loans
```{r out.width = 9, out.height = 5}
p <- model_table %>% 
  filter(is.na(max_dr12) == F) %>% 
  select(score, max_dr12) %>%
  mutate(score = round(score, 1),
         type_of_client = factor(if_else(max_dr12 == 0, "Good", "Bad"))) %>% 
  ggplot(.) + 
         geom_line(aes(x = score, col = type_of_client), adjust = 3, stat="density") + 
         labs(x = "Score", y = "Density", col = "Color") + theme_bw()
p
 
ggplotly(p, tooltip = c("score") )
 
```
 
 
 
 
Column {data-width=500 }
-------------------------------------   
 
 
###  Lift plot

```{r}
 
lift_data <- model_table %>% 
  filter(ref_period == 0) %>% 
  filter(is.na(max_dr12) == F) %>% 
  arrange(score) %>% 
  mutate(`Percent of bad` = cumsum(max_dr12)/sum(max_dr12) * 100) %>% 
  mutate(`Percent of population` = row_number()/ n() * 100 ) %>% 
  select(`Percent of bad`, `Percent of population`) %>% 
  mutate_all(., funs(round(., 2)))
 
 
lift_plot_gg <- ggplot(lift_data, aes(x = `Percent of population`, y = `Percent of bad`)) + 
  geom_line() + 
  xlab("Percent of population, %") + 
  ylab("Percent of bad, %") + 
  theme_bw() 
  #geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1))

ggplotly(lift_plot_gg)
 
 
 
```
 
 
### Kolmogorov - Smirnov
    
```{r out.width = 9, out.height = 5}
 
ks <- model_table %>% 
  mutate(max_dr12 = as.numeric(max_dr12)) %>% 
  filter(is.na(max_dr12) == F) %>% 
  select(score, max_dr12) %>%
  mutate(def = factor(if_else(max_dr12 == 0, "Good", "Bad"))) %>% 
  group_by(max_dr12) %>% 
  nest() %>% 
  mutate(data = map(data, ~ mutate(.x, cdf = cume_dist(score)))) %>% 
  unnest() %>% 
  sample_frac(0.3)
 
ks_gg <- ggplot(data = ks) + geom_line(aes(x = score, y =cdf, col = def)) + 
  theme_bw()
 
 
ggplotly(ks_gg, tooltip = c("score"))
```
 
Stability {data-orientation=rows}
=====================================     
 
Row {data-height=600}
-------------------------------------
 
### Risk stability dynamics by variables

```{r}
testpsi <- model_table %>%
    mutate(y_q = factor(quarter(consideration_date,with_year=TRUE)))
 
cols.to.factor <- sapply( testpsi, function(col) length(unique(col)) < 5 )
testpsi[ cols.to.factor] <- lapply(testpsi[ cols.to.factor] , factor)
 
ref  <- testpsi %>% 
  filter(ref_period == 1) %>% 
  mutate(y_q = quarter(consideration_date, with_year = T))
 
spisok_ref <- unique(ref$y_q)
 
 
vars <- models %>% 
  filter(model == params$data) %>% 
  distinct(var_x) %>% 
  pull() %>% 
  tolower()
 
for_risk_psi <- model_table %>% 
  filter(quarter(consideration_date, with_year = T) <= quarter(max(model_table$consideration_date), 
                                                               with_year = T) - 1) 
 
 
risk_psi_table <- map(vars, risk_psi, data = for_risk_psi) %>% 
  reduce(bind_rows) %>% 
  mutate(risk_psi = round(risk_psi, 2)) # round for better mouse on displaying 

#risk_psi_table <- risk_psi_table %>% filter(timeunit_q>max(spisok_ref))
risk_psi_table <- risk_psi_table %>% 
  filter(timeunit_q > max(spisok_ref))
 
# risk stability chart -------------------------------

plot_ly(risk_psi_table, x = factor(risk_psi_table$timeunit_q), 
                        y = risk_psi_table$risk_psi,
                        color = risk_psi_table$variable,
                        type = 'scatter',
                        mode = 'lines+markers') %>%
  add_lines(y=0.2,color=I("Black"),name='acceptable instability') %>%
  add_lines(y=0.1,color=I("Grey"),name='low instability') %>%
  layout(legend = list(orientation = 'h'))
 
```
 
Row {data-height=600}
-------------------------------------
 
### Stability dynamics by variables

```{r}
 
ne_ref  <- testpsi %>% 
  filter(ref_period == 0) %>% 
  mutate(y_q = quarter(consideration_date, with_year = T))%>%
  filter(y_q>max(spisok_ref))
 
spisok_neref<-unique(ne_ref$y_q)
 
psi_table <- data.frame(y_q= character(), vars= character(), psi = numeric(),stringsAsFactors=FALSE)
s=0
for (i in 1:length(vars)){
  for (j in 1:length(spisok_neref)){
    s <- s+1
    a <- as.factor(ref[,vars[i]][[1]])
    b <- as.factor(testpsi[testpsi$y_q==spisok_neref[j],vars[i]][[1]])
    psi_table[s,3]=round(psi(a,b),digits = 3)
    psi_table[s,2]=vars[i]
    psi_table[s,1]=spisok_neref[j]
  }
}
 
library(plotly)
 
psi_table <- psi_table %>% arrange(vars,y_q)
 
plot_ly(psi_table,x= factor(psi_table$y_q), y = psi_table$psi,color = psi_table$vars,type = 'scatter',mode = 'lines+markers') %>%
  add_lines(y=0.2,color=I("Black"),name='acceptable instability') %>%
  add_lines(y=0.1,color=I("Grey"),name='low instability') %>%
  layout(legend = list(orientation = 'h'))
 
```   
 
 
Model errors 
=====================================     
 
Column {}
-------------------------------------
 
### The correctness of the calculation  
```{r}
# if (test_expression) {
# statement1
# } else {
# statement2
# }

error_table_path <- paste0("//Rsb-assasp1/SASUSERS/DRKR/Common/common_share/scoring/dash_tables/errors_table/", 
                           params$data, 
                           ".sas7bdat")
 
if (file.exists(error_table_path)) {
 
    error_table <- read_sas(error_table_path, NULL)
 
    error_table %>%
        mutate(raznica_bin=if_else(raznica==0,"true","errors","errors")) %>%    
        group_by(raznica_bin) %>%    
        summarize(count = n()) %>%
        plot_ly(labels = ~raznica_bin, values = ~count,textposition = 'outside',
                marker = list(colors =c("rgba(207, 52, 52, 0.6)","rgba(50, 171, 96, 0.6)"))) %>%
              add_pie(hole = 0.81) %>%
              layout(title = paste0('The correctness of the calculation ', params$data),showlegend=T) %>%
              add_annotations(x=0,y=-0.05,
                          text = 'The correctness calculated as the difference 
                                  between scores in decision making system and theoretically model',
                          font = list(family = 'Arial', size = 15, color = 'rgb(126,150,150)'),
                          showarrow = FALSE)
} else {
  print("Model is not still implemented in production enviroment!")
}
```
 
Column {}
-------------------------------------
 
### The most common errors  
```{r}
 
# Here need to quote error table!
if (file.exists(error_table_path)) {
 
  error_table <- read_sas(error_table_path, NULL)
 
  top_differences <- error_table %>%
    filter(raznica != 0)  %>%
    mutate(raznica = as.character(raznica)) %>%
    group_by(raznica) %>%
    summarize(count = n()) %>% 
    top_n(5,count) %>% 
    arrange(count)
 
 
  xform <- list(categoryarray = top_differences$raznica)
 
  plot_ly(top_differences,
          x = top_differences$count,
          y= top_differences$raznica,
          type = 'bar', marker = list(color = 'rgba(207, 52, 52, 0.6)')) %>% 
          layout(yaxis = xform,title ='The most common errors',xaxis=list(title='count of score'))
 
} else {
    print("Waiting for implementation.")
  }
 
```
 
Variables description {data-orientation=rows}
=====================================     
 
Row {data-height=600}
-------------------------------------
 
### 

```{r}
models %>% 
  filter(model == params$data) %>% 
  select(Variable = var, Description) %>% 
  distinct() %>% 
  kableExtra::kable(.) %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))